gtsummary Reviewer Responses

### 2021-04-10 reviewer_responses/gtsummary_review_2021-03-23.Rmd
updates

---
title: "gtsummary Reviewer Responses"
author: "Daniel Sjoberg, Karissa Whiting, Mike Curry"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: sandstone
    toc: yes
    toc_float: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

3. Package Testing

>>>>

---
title: "gtsummary Reviewer Responses"
author: "Daniel Sjoberg, Karissa Whiting, Mike Curry"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: sandstone
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

@@

3. The gtsummary developers use testthat as their testing suite, and codecov to measure and report their test coverage. On Github, they report a 93% test coverage which, at first glance, is very impressive. Unfortunately, I do not think that those tests follow best practices, and I am not convinced that the 93% tells us much. After looking at a few tests I did a quick grep and found that about 75% of expectations in the test folder were either expect_message, expect_error, or expect_warning (please correct me if this is wrong!). Most of the time, the tests only seem to make sure that no error is produced.
